### 2017-12-13 readme.rmd
adjusted figure legend

The primary explanation Feuda *et al.* 2017 provide for accepting some results and rejecting others is their posterior predictive (PP) analyses of model adequacy. They calculated PP for only the Whelan-Opisthokont and Chang matrices (Figures 2-3, top two rows). Based on these scores they rejected the results of the GTR-G analyses (Figures 2-3, left pane) and analyses that had not been recoded. This left six cells that are the focus of their primary conclusions (Figures 2-3, right panel, top two rows, right 3 cells).

@@

*Figure 4 - Detailed examination of the analysis subset (indicated in upper right pane) that is the focus of the conclusions by Feuda et al. These are the six recoded CAT-GTR+G analyses with posterior predictive (PP) scores. The presented statistics for these six cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence), and five PP scores (where lower absolute value indicates better model adequacy). Only one analysis provides significant support for Porifera-sister. It isn't the most adequate by any of the PP scores, and showed the poorest convergence according to Maxdiff. Recodings are: None- K - KGB-6, D - Dayhoff-6, and S- SR-6.*

A variety of statistics from Feuda *et al.* 2017 for these six cells are presented in Figure 4. The first thing to note is that only one of these six analyses provides significant support for Porifera-sister. This is for the SR-6 recoded Whelan-Opisthokont matrix, shown in green in Figure 4. Given the similarity of these six analyses, the fact that only one supports Porifera-sister calls into serious question the robustness of support for Porifera-sister.

>>>>

The primary explanation Feuda *et al.* 2017 provide for accepting some results and rejecting others is their posterior predictive (PP) analyses of model adequacy. They calculated PP for only the Whelan-Opisthokont and Chang matrices (Figures 2-3, top two rows). Based on these scores they rejected the results of the GTR-G analyses (Figures 2-3, left pane) and analyses that had not been recoded. This left six cells that are the focus of their primary conclusions (Figures 2-3, right panel, top two rows, right 3 cells). A variety of statistics from Feuda *et al.* 2017 for these six cells are presented in Figure 4.

@@

*Figure 4 - Detailed examination of the analysis subset (indicated in upper right pane) that is the focus of the conclusions by Feuda et al. These are the six recoded CAT-GTR+G analyses with posterior predictive (PP) scores. The presented statistics for these six cells are posterior probability of Porifera-sister, Maxdiff (with lower scores indicating better convergence), and five PP scores (where lower absolute value indicates better model adequacy). Only one analysis provides significant support for Porifera-sister (shown in green). It is not the most adequate analysis by any of the PP scores, and showed the poorest convergence according to Maxdiff. Recodings are: K - KGB-6, D - Dayhoff-6, and S- SR-6.*

The first thing to note is that only one of these six analyses provides significant support for Porifera-sister. This is for the SR-6 recoded Whelan-Opisthokont matrix, shown in green in Figure 4. Given the similarity of these six analyses, the fact that only one supports Porifera-sister calls into serious question the robustness of support for Porifera-sister.
